Future challenges for Research Software Engineering

### 2025-05-12 future_challenges_for_RSEng.tex
now most ideas boxes worked in

\section{What is in this future for RSEs and where to go from here?}
FG-NOTE: I think we can use this part to wrap things a bit up, and describe how this future then looks like.

GC-NOTE: Shall we add another story box here?

GC-NOTE: RSE develop together with and for scientists.
Better software leads to better research,
better research leads to more better software.

>>>>

\section{What is in this future for RSEs and where to go from here?}
FG-NOTE: I think we can use this part to wrap things a bit up, and describe how this future then looks like.
GC-NOTE: Shall we add another story box here? Ideas what we write here?

Digitalisation will lead to changes in the way societies interact and therefore will translate
into changes in how academia perceives itself. The differentiation of job profiles in academia,
that has started with profiles such as the RSE will continue. Societies will be facing new questions, that arise
from technologies such as generally available AI systems. RSEs will very likely be doing different work,
than what they are doing today, but their core task of enhancing the scientific output of researchers, other human
beings, will stay the same.
They will still develop software artifacts together with scientists,
since Better software leads to better research,
better research leads to more better software.
